\documentclass[12pt]{article}


\begin{document}



\section{Disease:-}


A disease is an abnormal condition that affects the structure or function of all or part of an organism without being caused by an external harm.Medical illnesses having distinct indications and symptoms are commonly referred to as diseases. External influences, such as infections, or internal dysfunctions can both cause disease. Internal immune system dysfunctions, for example, can result in a wide range of diseases, including immunodeficiency, hypersensitivity, allergies, and autoimmune disorders.

\section{Health care system:-}

A health system, also known as a health care system or a healthcare system, is a collection of people, institutions, and resources that provide health care services to satisfy the requirements of certain populations.Health care is the maintenance or improvement of health via the prevention, diagnosis, treatment, amelioration, or cure of disease, illness, injury, and other physical and mental impairments in people. Health care is delivered by health professionals and allied health fields. Medicine, dentistry, pharmacy, midwifery, nursing, optometry, audiology, psychology, occupational therapy, physical therapy, athletic training, and other health professions are all part of health care. It includes work done in providing primary care, secondary care, and tertiary care, as well as in public health.

\section{Evolution of health care system:-}

Healthcare in the world went from a rudimentary system of folk medicines and itinerant doctors with little training to a complex, scientific, technological, and bureaucratic system known as the "medical industrial complex" between the years 1750 and 2000. The complex is based on medical science and technology, as well as medical professionals' authority. The acceptance of the "germ theory" as the cause of disease, the professionalisation of doctors, technological improvements in disease treatment, the creation of big institutions of medical training and healing, and the introduction of medical insurance are all part of this complex's growth. During this time, governmental institutions, restrictions, health-care systems, drug regulations, and medical insurance all evolved. Recently, the healthcare sector has experienced an increase in the number of firms whose primary business is healthcare.

\section{Old medical equipments:-}

Syringe:-
Although syringes are still used today, this one was unique. It was much larger than the hypodermics we use today, with its long, thin tube and pump. It was used to inject mercury as a therapy for syphilis in the 1500s, which was commonly contracted by amorous sailors on the high seas. The good news is that you weren't stabbed with such a large syringe. Unfortunately, because it was a urethral syringe, the injection went straight into the penis through its natural entrance. Worse, the mercury typically killed people before the syphilis problems did

\section{CT scan:-}
A CT scan combines a sequence of X-ray images taken from various angles around your body with computer processing to create cross-sectional images (slices) of the bones, blood arteries, and soft tissues within your body. CT scan images contain more information than standard X-rays.A CT scan can be used for a variety of purposes, but it's especially useful for quickly examining patients who may have internal injuries as a result of vehicle accidents or other sorts of trauma. A CT scan can visualise almost every region of the body and is used to diagnose sickness or injury as well as plan medical, surgical, or radiation treatment.


\end{document}